---
title: "A6"
author: "Le Yang"
date: "10/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Troy, NY's vacant property and male asian demography

This is Le Yang's assignment 6 for Spatial Analysis.The first map shows the vacancy unit within Albany county. The second map shows the number of male Asians among the total number of Asians in the same area. 

```{r load packages, message=FALSE, echo=FALSE, warning=FALSE,results='hide',fig.show='hide'}
library(leaflet)
library(sf)
library(tidyverse)
library(tidycensus)
library(ggthemes)
library(ggspatial)
library(htmlwidgets)
library(tidytransit)
library(magrittr)
library(dplyr)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE,results='hide',fig.show='hide'}
Albany_Vacancy <- get_decennial(geography = "block",
                          state = "NY", county = "Albany",
                          year = 2010,
                          output = "wide",
                          variables = c(tot_unit = 'H001001',
                                        tot_vac = 'H005001'),
                          geometry = TRUE)
```

```{r, echo=FALSE, message=FALSE}
Albany_Vacancy <- Albany_Vacancy %>%
  mutate(pct_Vacancy = tot_vac / tot_unit) %>%
  filter(tot_unit>0)
```

```{r, echo=FALSE, message=FALSE, fig.show='hide',results='hide', warning=FALSE}
NY_state_plane <- "+proj=tmerc +lat_0=40 +lon_0=-76.58333333333333 +k=0.9999375 +x_0=249999.9998983998 +y_0=0 +ellps=GRS80 +datum=NAD83 +to_meter=0.3048006096012192 +no_defs"

ggplot(Albany_Vacancy) +
  annotation_map_tile(zoomin = 0, progress = "none", type = "stamenbw") +
  geom_sf(color = NA, aes(fill = pct_Vacancy), alpha = 0.7) +
  coord_sf(crs = NY_state_plane) +
  scale_fill_continuous(low="cornsilk", high="darkgreen", 
                       na.value=NA,
                       name = "Percent of Unit\nidentifying as Vacant",
                       breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1),
                       labels = c("0", "20%", "40%", "60%", "80%", "100%")) +
  theme_void() 
```

```{r, echo=FALSE, message=FALSE, fig.show='hide', warning=FALSE, results='hide'}
NY_Vacancy_palette <- colorNumeric(c("cornsilk", "darkgreen"), Albany_Vacancy$pct_Vacancy)

Vacancy_map1 <- leaflet(Albany_Vacancy) %>%
  addProviderTiles("Stamen.TonerLite") %>%
  addPolygons(stroke = FALSE, fillOpacity = 0.7,
    color = ~NY_Vacancy_palette(pct_Vacancy)) %>%
  addLegend("bottomright", pal = NY_Vacancy_palette, values = ~pct_Vacancy,
    title = "Percent of unit<br/>identifying as vacancy",
    labFormat = labelFormat(suffix = "%",
                            transform = function(x) 100 * x),
    opacity = 1)

Vacancy_map1
```

```{r, echo=FALSE, message=FALSE, fig.show='hide', warning=FALSE, results='hide'}
Vacancy_map2 <- leaflet(Albany_Vacancy) %>%
  addProviderTiles("Stamen.TonerLite") %>%
  addPolygons(color = ~NY_Vacancy_palette(pct_Vacancy), stroke = FALSE, fillOpacity = 0.7,
              highlightOptions = highlightOptions(fillColor = "darkorange", fillOpacity = 0.9),
              label = "This is a label",
              popup = "This is a popup") %>%
    addLegend("bottomright", pal = NY_Vacancy_palette, values = ~pct_Vacancy,
    title = "Percent of unit<br/>identifying as vacancy",
    labFormat = labelFormat(suffix = "%",
                            transform = function(x) 100 * x),
    opacity = 1)

Vacancy_map2
```

##This map shows the vacancy number in the area. What we can find is that the area near Middleburgh is the area with most vacant properties.
```{r, echo=FALSE, message=FALSE}
Vacancy_map3 <- leaflet(Albany_Vacancy) %>%
  addProviderTiles("Stamen.TonerLite") %>%
  addPolygons(color = ~NY_Vacancy_palette(pct_Vacancy), stroke = FALSE, fillOpacity = 0.7,
              highlightOptions = highlightOptions(fillColor = "darkorange", fillOpacity = 0.9),
              label = Albany_Vacancy$NAME,
              popup = paste("Total unit: ", Albany_Vacancy$tot_unit, "<br/>",
                            "Vacancy unit: ", Albany_Vacancy$tot_vac, " (", 
                            round(Albany_Vacancy$pct_Vacancy * 100, 1), "%)", sep = "")) %>%
    addLegend("bottomright", pal = NY_Vacancy_palette, values = ~pct_Vacancy,
    title = "Percent of unit<br/>identifying as vacant",
    labFormat = labelFormat(suffix = "%",
                            transform = function(x) 100 * x),
    opacity = 1)

Vacancy_map3
```

```{r, echo=FALSE, message=FALSE, warning=FALSE,results='hide',fig.show='hide'}
saveWidget(Vacancy_map3, file="tory_vacancy.html")
```



```{r, echo=FALSE, message=FALSE, warning=FALSE,results='hide',fig.show='hide'}
maleasia_Albany <- get_acs(geography = "tract", county = "Albany", state = "NY", 
                           year = 2019, survey = "acs5",
                           variables = c(tot_asia = "B01001D_001", male_asia = "B01001D_002"),
                           output = "wide", geometry = TRUE) 
```

```{r, echo=FALSE, message=FALSE}
maleasia_Albany <- maleasia_Albany %>%
  select(-tot_asiaM, -male_asiaM) %>%
  filter(tot_asiaE > 0) %>%
  mutate(pct_maleasia = round(100 * male_asiaE / tot_asiaE, 1))
```

##This map shows the male asian within total asian population in the area. As we can see, around Albany city and Troy city, most of the asians are males.
```{r, echo=FALSE, message=FALSE}
maleasia_palette <- colorNumeric(c("pink", "lightblue"),
                                maleasia_Albany$pct_maleasia)

maleasia_map <- leaflet(maleasia_Albany) %>%
  addProviderTiles("Stamen.TonerLite") %>%
  addPolygons(fillColor = ~maleasia_palette(pct_maleasia), weight = 1, color = "gray", fillOpacity = 0.7,
              highlightOptions = highlightOptions(fillColor = "yellow", fillOpacity = 0.9),
              label = maleasia_Albany$NAME,
              popup = paste("Total asian: ", maleasia_Albany$tot_asiaE, "<br/>",
                            "Male asian: ", maleasia_Albany$male_asiaE, " (",
                            maleasia_Albany$pct_maleasia, "%)", sep = "")) %>%
    addLegend("bottomright", pal = maleasia_palette, values = ~pct_maleasia,
    title = "Percent of male<br/>in asian population",
    labFormat = labelFormat(suffix = "%"),
    opacity = 1)

maleasia_map
```

